---
title: "Basic Inferencial Data Analysis"
author: "Vijayeshswari Palakurthi"
date: "6/5/2020"
output: pdf_document
---
**Data and packages:**
Let’s load the “ToothGrowth” data (available in the datasets package) and some relevant library packages used in this project

```{r warning=F}
library(datasets) 
library(ggplot2) 
library(reshape2) 
library(dplyr) 
data(ToothGrowth)
```
Here are some explanations from the help page of the package:

**Description:**
The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC).

**Format:**
A data frame with 60 observations on 3 variables.
[,1] len numeric Tooth length [,2] supp factor Supplement type (VC or OJ). [,3] dose numeric Dose in milligrams/day

**Exploratory analysis:**
Let’s create a boxplot of the growth vs. the delivery method.

```{r}
g = ggplot(ToothGrowth, aes(supp, len,fill =supp)) 
g =g	+geom_boxplot ()
g

```
This is a boxplot using the 2 variables dose and delivery method:

```{r}
g = ggplot(ToothGrowth, aes(supp, len,fill =supp)) 
g =g	+geom_boxplot ()
g =g	+facet_grid (. ~ dose) 
g

```
**Some first observations:**
* The growth seems to increase with the dose
* The growth seems to be more important when the guinea pig is fed orange juice instead of vitamin C, but this effect seems to dissipate as the dose increases.


**Tooth growth comparison:**
We’ll use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. As the number of observations is small, let’s use Gossett’s T tests for our analysis.

**Conclusion:**
The difference between the means is significant between the guinea pigs receiving a 0.5mg/day dose and a 2 mg/day dose.
In the 2 other cases, the hypothesis between a difference in the means can’t be confirmed when using a 95% confidence interval.





